---
title: "Corruption and Accountability Mechanisms"
author: Mariam Sanjush and Roberto Martinez B. Kukutschka
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Descriptive


## Variables

| Names           | Scale      | Description                                             |
|-----------------|------------|---------------------------------------------------------|
| COC score       | Continuous | Control of corruption score                             |
| Trade           | Continuous | Share of trade of the GDP                               |
| Urban           | Continuous | Proportion of urban Population                          |
| GDPPC           | Continuous | GDP per capita                                          |
| Education       | Continuous | Gross enrollment ratio is the ratio of total enrollment |
| Competitiveness | Continuous | Taxes payable by businesses                             |
| Year            | Integer    | Year identifier                                         |
| Country         | Nominal    | Country identifier                                      |
| Foia            | Dummy      | Freedom of Information                                  |
| Aca_press       | Dummy      | Existence of Anti-Corruption Agency                     |                                     


#Dont know why the i can not plot the figure???

```{r euro, echo=FALSE}
plot (euro)
```


\begin{table}[!htbp] \centering 
  \caption{Descriptive statistic for all the variables} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
Statistic & \multicolumn{1}{c}{N} & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{St. Dev.} & \multicolumn{1}{c}{Min} & \multicolumn{1}{c}{Max} \\ 
\hline \\[-1.8ex] 
Year & 532 & 2,005.000 & 5.482 & 1,996 & 2,014 \\ 
Trade & 529 & 105.011 & 53.175 & 37.496 & 374.148 \\ 
GDPPC & 531 & 571,574,423,722.000 & 823,194,143,528.000 & 7,965,375,795.000 & 3,526,973,256,303.000 \\ 
Education & 496 & 103.146 & 13.709 & 74.350 & 163.101 \\ 
Competitiveness & 270 & 222.191 & 141.176 & 55.000 & 930.000 \\ 
Urban & 532 & 71.681 & 11.993 & 49.695 & 97.818 \\ 
Cocscore & 448 & 1.027 & 0.849 & $-$0.820 & 2.586 \\ 
Foia & 532 & 0.276 & 0.448 & 0 & 1 \\ 
Aca\_pres & 532 & 0.457 & 0.499 & 0 & 1 \\ 
\hline \\[-1.8ex] 
\end{tabular} 
\end{table}



# Analysis
Fixed Effects panel analysis

\begin{table}[!htbp] \centering 
  \caption{Fixed-Effects panel analysis} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{2}{c}{\textit{Dependent variable:}} \\ 
\cline{2-3} 
\\[-1.8ex] & \multicolumn{2}{c}{cocscore} \\ 
\\[-1.8ex] & (1) & (2)\\ 
\hline \\[-1.8ex] 
 foia & $-$0.299$^{**}$ &  \\ 
  & (0.140) &  \\ 
  & & \\ 
 aca\_pres &  & $-$0.245$^{***}$ \\ 
  &  & (0.042) \\ 
  & & \\ 
 gdppc & 0.000$^{***}$ & 0.000$^{***}$ \\ 
  & (0.000) & (0.000) \\ 
  & & \\ 
 education & 0.001 & 0.001 \\ 
  & (0.001) & (0.001) \\ 
  & & \\ 
 competitiveness & 0.0004$^{**}$ & 0.0003$^{*}$ \\ 
  & (0.0002) & (0.0001) \\ 
  & & \\ 
 trade & $-$0.0001 & 0.0002 \\ 
  & (0.001) & (0.001) \\ 
  & & \\ 
 urban & $-$0.038$^{***}$ & $-$0.033$^{***}$ \\ 
  & (0.012) & (0.011) \\ 
  & & \\ 
\hline \\[-1.8ex] 
Observations & 239 & 239 \\ 
R$^{2}$ & 0.144 & 0.248 \\ 
Adjusted R$^{2}$ & 0.123 & 0.213 \\ 
F Statistic (df = 6; 205) & 5.730$^{***}$ & 11.279$^{***}$ \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{2}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table} 



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
